How did local health infrastructure and socio-political factors within different states and counties in the United States affect the disparities in COVID-19 outcomes, and what lessons can be learned for more targeted public health preparedness and response strategies in future pandemics?

### 2024-02-12 outputs/paper/paper.qmd
updated most of discussion

@@

## Data cleaning

@@

>>>>

*The introduction is self-contained and tells a reader everything they need to know including: 1) broader context to motivate; 2) some detail about what the paper is about; 3) a clear gap that needs to be filled; 4) what was done; 5) what was found; 6) why it is important; 7) the structure of the paper. A reader should be able to read only the introduction and know what was done, why, and what was found. Likely 3 or 4 paragraphs, or 10 per cent of total. The estimand is clearly stated in the introduction.*

@@

*A thorough discussion of measurement, relating to the dataset, is provided in the data section.*

@@

# Conclusion 
\newpage
